Improving the modelling of tempo and phoneme duration

### 2017-03-14 Paper/Paper_v1.tex
Some additions to section on Verbmobil.

\chapter{Corpora}
\section{Verbmobil}
The Verbmobil corpus is a database of spontaneous speech containing a collection of appointment making dialogs, fully transliterated and annotated. We used 286 recordings from the last verbmobil phase (Verbmobil II) created by 131 speakers. The total VMII corpus used amounts to 11783 conversational turns representing recorded speech time of 15,5 hours. The ``symbolic data`` corresponding to each turn (e.g.phonetic transcription, segmentation, labeling, etc.) is captured in so-called ``par files``, representing files in the ``BAS Partitur Format`` \cite{Burger}.

Following natural rules, the tipical characteristic of data in this corpus is that speech rate often varies significantly inside a speech turn. This results in the challenge of finding an appropriate description for the speech rate across the corpus to be used for modeling the phoneme durations. We handle the issue of the speech rate separately in chapter 5.

Another challenge resulting from the structure of this corpus as collection of dialogs is the speaker variation. The exact values of the phoneme duration coordinates vary across speakers, as one can see in Fig. ??? for the case of /a/.

>>>>

\chapter{Corpora}
\section{Verbmobil}
The Verbmobil corpus is a database of spontaneous speech containing a collection of appointment making dialogs, fully transliterated and annotated. This was an important point in selecting this database for our purpose, as phoneme duration is influenced by many factors, and the Verbmobil textual database provides most of them. We used 286 recordings from the last verbmobil phase (Verbmobil II) created by 131 speakers. The total VMII corpus used amounts to 11783 conversational turns representing recorded speech time of 15,5 hours. The ``symbolic data`` corresponding to each turn (e.g.phonetic transcription, segmentation, labeling, etc.) is captured in so-called ``par files``, representing files in the ``BAS Partitur Format`` \cite{Burger}.

Drawbacks of this database come mainly from the characteristics of spontaneous speech. Following natural rules, speech rate often varies significantly inside a speech turn. One starts his turn at a normal speech rate, then gets to a point where he/she hesitates and gets slower, like when weighting different transport means to get to the appointment they are to agree upon. This results in the challenge of finding an appropriate description for the speech rate to be used for modeling phoneme durations across the corpus. We handle this issue of speech rate separately in chapter 5. Another challenge resulting from the structure of this corpus as a collection of dialogs is speaker variation. The exact coordinates of the phoneme durations vary across speakers, as one can see in Fig. ??? for the case of /a/.
